\section{Protocol summary}

% TODO
Describe stdin, stdout, json and shit...

\subsection{Types}

% TODO Speak about types

Provided types are semantic and do not define their underlying storage. Enums values are specified like so \texttt{enum \{ value-1, ..., value-n \}} and are to be provided in commands as strings.

\subsection{Command summary}

All commands contain at least a \texttt{command} field.

\begin{center}
\begin{tabu} to\linewidth {X[l, -2] | X[l, 4] | X[l, -1] | X[c, -1]}
    Command
        & Description
        & Parameters
        & Read-only \\ \hline \hline
    \texttt{reset}
        & Resets all internal state.
        &
        & no \\
    \texttt{unserialize}
        & Initializes the application state with a saved game.
        & format, value
        & no \\
    \texttt{serialize}
        & Serializes the game state.
        &
        & yes \\
    \texttt{generate\_moves}
        & Generates all moves for a board piece.
        & x, y
        & yes \\
    \texttt{check\_move}
        & Checks if a move is valid.
        & from\_x, from\_y, to\_x, to\_y
        & yes \\
    \texttt{move}
        & Moves a piece on the board updating internal states.
        & from\_x, from\_y, to\_x, to\_y
        & yes \\
\end{tabu}
\end{center}

\subsection{Errors}

All responses contain at least a \texttt{status} field with either \texttt{ok} or \texttt{nok}. In case the \texttt{status} is \texttt{nok}, the response always contains an \texttt{error} field containing and error code (string) and an \texttt{error\_msg} field containing more information about the error.\\
Aside from command specific errors, some errors should always be handled when reading a \texttt{nok} response:

\begin{ResponseErrors}
    \texttt{invalid\_json}
        & Could not parse the provided json. \\
    \texttt{invalid\_command}
        & Invalid command provided. \\
    \texttt{invalid\_type}
        & The value of a field is invalid (invalid data type, value outside of enum bounds; etc.). \\
    \texttt{missing\_field}
        & A mandatory type was missing for the command. \\
\end{ResponseErrors}

\newpage
\section{Protocol commands}

\input{parts/proto01-reset.tex}
\newpage
\input{parts/proto02-unserialize.tex}
\newpage
\input{parts/proto03-serialize.tex}
\newpage
\input{parts/proto04-generate_moves.tex}
\newpage
\input{parts/proto05-check_move.tex}
\newpage
\input{parts/proto06-move.tex}
